Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-25 WSSSPE1_report/WSSSPE1_summary_report.tex
Minor change.

On the other hand, there are companies
that fund larger GPL-licensed software projects~\cite{Blatt_WSSSPE}
that insists that the university projects they fund 
also produce code with GPL licensing.
They do not accept BSD-like licenses since they argue that
other companies then may choose to build closed commercial
codes on they software they funded, rather than encouraging 
the community to contribute freely and thus ensuring software 
sustainability for the community.

>>>>

On the other hand, there are companies
that fund larger GPL-licensed software projects~\cite{Blatt_WSSSPE}
and insist that the university projects they fund 
also produce code with GPL licensing.
They do not accept BSD-like licenses since they argue that
other companies then may choose to build closed commercial
codes on they software they funded, rather than encouraging 
the community to contribute freely and thus ensuring software 
sustainability for the community.
